---
title: "Statistical Inference Week 2, Part 1: Simulation Exercise Instructions"
author: "Kaushik Basu"
date: "December 23, 2017"
output: word_document
fontsize: 10pt
---

The exponential distribution can be simulated in R with rexp(n, lambda) where lambda is the rate parameter. The mean of exponential distribution is 1/lambda and the standard deviation is also also 1/lambda. Set lambda = 0.2 for all of the simulations. In this simulation, you will investigate the distribution of averages of 40 exponential(0.2)s. Note that you will need to do a thousand or so simulated averages of 40 exponentials.
Illustrate via simulation and associated explanatory text the properties of the distribution of the mean of 40 exponential(0.2)s. 

##### Question 1 
Show the sample mean and compare it to the theoretical mean of the distribution.
##### Question 2 
Show how variable the sample is (via variance) and compare it to the theoretical variance of the distribution.
```{r}
lambda = 0.2
n = 40
nsms = 1:1000
set.seed(820)
means <- data.frame(x = sapply(nsms, function(x) {mean(rexp(n, lambda))}))
head(means)
```

```{r}
mean(means$x)
```
```{r}
sd(means$x)
```
```{r}
(1/lambda)/sqrt(40)
```
```{r}
var(means$x)
```
```{r}
((1/lambda)/sqrt(40))^2
```
Center of the distribution: 4.9988. Expected center: 5.0. The mean of the means of the exponential of 1000 simulations of 40 exponential(0.2)s is 4.9988, which is very close to the expected mean of 1/0.2 = 5.0.

Variability of the distibution. The standard deviation of 0.7909 is also close to the expected standard deviation of 0.79056

##### Question 3
Show that the distribution is approximately normal.

Below is a histogram plot of the means of the 1000 simulations of rexp(n, lambda). It is overlaid with a normal distribution with mean 5 and standard deviation 0.7909. Yes, the distribution of our simulations appears normal.

```{r}
library(ggplot2)
ggplot(data = means, aes(x = x)) + 
    geom_histogram(aes(y=..density..), fill = I('#00e6fa'), 
                   binwidth = 0.20, color = I('black')) +
    stat_function(fun = dnorm, arg = list(mean = 5, sd = sd(means$x)))
     
```

##### Question 4
Evaluate the coverage of the confidence interval
```{r}
mean(means$x) + c(-1,1)*1.96*sd(means$x)/sqrt(nrow(means))
```


